---
title: "HW4"
format: html
editor: visual
---

## Task 1: Conceptual Questions

### 1. What is the purpose of the lapply() function? What is the equivalent purrr function?

Apply functon to lists.map()

### 2. Suppose we have a list called my_list. Each element of the list is a numeric data frame (all columns are numeric). We want use lapply() to run the code cor(numeric_matrix, method = "kendall") on each element of the list. Write code to do this below! (I’m really trying to ask you how you specifymethod = "kendall" when calling lapply())

lapply(x=my_list,FUN=function(x){temp\<-cor(x, method = "kendall")})

### 3. What are two advantages of using purrr functions instead of the BaseR apply family? purrr gives us a bit cleaner/more consistent way to apply functions to objects

purrr functions also give a shorthand way to make anonymous functions

### 4. What is a side-effect function?

A side-effect function in programming is a function that performs operations other than returning a value,like print()

### 5. Why can you name a variable sd in a function and not cause any issues with the sd function?

When you call a function, it creates temporary function environments

## Task 2

### 1

```{r}

getRMSE<- function(x,y){
  x[is.na(x)] <- mean(x, na.rm = TRUE)
  y[is.na(y)] <- mean(y, na.rm = TRUE)
  rmse <- mean((x-y)^2)^(1/2)
}

```

### 2

```{r}
set.seed(10)
n <- 100
x <- runif(n)
resp <- 3 + 10*x + rnorm(n)
pred <- predict(lm(resp ~ x), data.frame(x))
 
rmse<-getRMSE(resp,pred)
print(rmse)
 
resp[2] <-NA
pred[5] <-NA
 
rmse<-getRMSE(resp,pred)
print(rmse)
 
 
```

### 3

```{r}
getMAE<- function(x,y){
  x[is.na(x)] <- mean(x, na.rm = TRUE)
  y[is.na(y)] <- mean(y, na.rm = TRUE)
  mae <- mean(abs(x-y))
}
```

### 4

```{r}
set.seed(10)
n <- 100
x <- runif(n)
resp <- 3 + 10*x + rnorm(n)
pred <- predict(lm(resp ~ x), data.frame(x))

mae<-getMAE(resp,pred)
print(mae)

resp[2] <-NA
pred[5] <-NA

mae<-getMAE(resp,pred)
print(mae)
```

### 5

```{r}
wrapper <- function(x, y) {
  if (!is.vector(x) | !is.vector(y)) {
    print("We need vectors")
    return()
  } else if ((!is.atomic(x) & !is.numeric(x)) | (!is.atomic(y) & !is.numeric(y))) {
    print("We need atomic or numeric vectors")
    return()
  } else {
    rmse <- getRMSE(x, y)
    mae <- getMAE(x, y)
    result <- c(rmse, mae)
    names(result) <- c("rmse", "mae")
    return(result)
  }
}

```

### 6

```{r}
 set.seed(10)
 n <- 100
 x <- runif(n)
 resp <- 3 + 10*x + rnorm(n)
 pred <- predict(lm(resp ~ x), data.frame(x))

 result<-wrapper(resp,pred)

 result
 
resp[2] <-NA
pred[5] <-NA

result<-wrapper(resp,pred)
print(result)


```

## Task 3- Querying an API and a Tidy-Style Function

```{r}
library(httr)
library(jsonlite)
```

### 1

```{r}
api_key <- "307b37fc38da410492f71b843cd9c7a9"

response <- GET("https://newsapi.org/v2/everything", query = list(q = "tesla",  apiKey = api_key))

parsed <- fromJSON(rawToChar(response$content))

parsed1 <- as.data.frame(parsed)

```

### 2

```{r}
query <- function(title, start,end,key){
  
  api_key <- key

  response <- GET("https://newsapi.org/v2/everything", query = list(q = title, from=start, to=end, apiKey = api_key))

  parsed <- fromJSON(rawToChar(response$content))

  parsed1 <- as.data.frame(parsed)
  
  return=parsed1

}

google<-query("google","2024-06-01","2024-06-01","307b37fc38da410492f71b843cd9c7a9")

tesla<-query("tesla","2024-06-01","2024-06-01","307b37fc38da410492f71b843cd9c7a9")

```
